\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
minor

%\item
A third option for Alice is to earn a PhD in cryptography, and design
and implement specialized, efficient \mpc protocols (similar
to~\cite{shafindss,wu,minionn}) for her tasks.
%\end{tiret}
%In our work, we achieve the best of all the above options.

@@

\subsubsection*{\tool}
\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

>>>>

%\item
A third option for Alice is to earn a PhD in cryptography, and design
and implement specialized, efficient \mpc protocols (similar
to~\cite{shafindss,wu,minionn,valeriaMatrix}) for her tasks.
%\end{tiret}
%In our work, we achieve the best of all the above options.

@@

%\subsubsection*{\tool}
%\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
These papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
the surprising fact that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.
